InteroceptionStudy_GPValidation

### 2021-08-24 IAPS_PREPROCESSING_2021_1.Rmd
heart rate bio

tmp.df4$trigger2<- tmp.df4$trigger

@@

unique(tmp.df4$trigger2)

@@

db_beh2$triggeracq<- db_beh2$trigger
unique(db_beh2$ssid)

@@

@@

```{r}
read_leda <- function(flnm) {
  data.table::fread(flnm) %>% 
    mutate(filename = flnm)
}

@@

db_leda$trigger<- as.numeric(db_leda$Event.NID)
unique(db_leda$trigger)
db_leda$ssid<- as.numeric(substr(db_leda$filename, 13,15))
colnames(tmp.df4_sum)
colnames(db_leda)
nrow(tmp.df4_sum)
nrow(db_leda)
colnames(tmp.df4_sum)
tmp.df4_sum2<- subset(tmp.df4_sum,tmp.df4_sum$tNo != -7)
tmp.df4_sum2<- tmp.df4_sum2%>%
  arrange(ssid, time, tNo)%>%
  group_by(ssid)%>%
  mutate(order = 1:224)

db_leda2<- subset(db_leda, db_leda$trigger != -7)
db_leda2<- db_leda2%>%
  arrange(ssid, Event.Nr)%>%
  group_by(ssid)%>%
  mutate(order = 1:224)

tmp.df4_sum_fullt<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
tmp.df4_sum_full_backup<- tmp.df4_sum_full

@@

tmp.df4_sum_full<- tmp.df4_sum_full%>%
  arrange(ssid, tNo)
```

@@

tmp.df4_sum_full_stim<- subset( tmp.df4_sum_full,  tmp.df4_sum_full$screencontent == 'stim')

levels(as.factor(tmp.df4_sum_full_stim$Event.Name))
tmp.df4_sum_full_stim<- subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$gaze_valid_prop> .85)
colnames(tmp.df4_sum_full_stim)

@@

ggplot(tmp.df4_sum_full_stim, aes(arousal_c, log1p(mean_fix_dur)))+
  geom_point()+
  geom_smooth(method = 'lm')

@@

```{r}
colnames(tmp.df4_sum_full)

@@

db_leda_bio$trigger<- as.numeric(db_leda_bio$Event.NID)
db_leda_bio$ssid<- as.numeric(substr(db_leda_bio$filename, 3,5))

colnames(tmp.df4_sum_full)
unique(tmp.df4_sum_full$trigger)

tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full, tmp.df4_sum_full$ssid>303)
# tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full_bio, tmp.df4_sum_full_bio$trigger!= -7)

levels(as.factor(tmp.df4_sum_full_bio$ssid))
unique(tmp.df4_sum_full_bio$trigger)
levels(as.factor(db_leda_bio$ssid))

db_leda_bio$ssid<- as.factor(db_leda_bio$ssid)
db_leda_bio$trigger<- as.factor(db_leda_bio$trigger)
db_leda_bio$order<- db_leda_bio$Event.Nr
tmp.df4_sum_full_bio$ssid<- as.factor(tmp.df4_sum_full_bio$ssid)
tmp.df4_sum_full_bio$trigger<- as.factor(tmp.df4_sum_full_bio$trigger)

@@

@@

tmp.df4_sum_full_bio%>%
  arrange(ssid, tNo, order)
db_leda_bio<- db_leda_bio%>%
  arrange(ssid, order)

tmp.df4_sum_full_bio$trigger<- tmp.df4_sum_full_bio$tNo
tmp.df4_sum_full_bio$trigger<- if_else(tmp.df4_sum_full_bio$screencontent == 'fixation', 100,
                                       if_else(tmp.df4_sum_full_bio$screencontent == 'ValenceResp', 101,
                                               if_else(tmp.df4_sum_full_bio$screencontent == 'IntResp', 102, tmp.df4_sum_full_bio$tNo)))

unique(tmp.df4_sum_full_bio$trigger)

tmp.df4_sum_full_biot<-left_join(tmp.df4_sum_full_bio, db_leda_bio, by = c("order", "ssid", "trigger"))
(db_leda_bio$trigger)

@@

ggplot(subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308), aes(TTP.AmpSum.y, arousal))+
  geom_point()+
  geom_smooth(method = 'lm', se = T)
ggplot(subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308 & tmp.df4_sum_full_biot$TTP.AmpSum.y> 0), aes( TTP.AmpSum.y, arousal))+
  geom_point()+
  geom_smooth(method = 'lm', se = T)
tmp.df4_sum_full_biot1 <-subset(tmp.df4_sum_full_biot, tmp\.df4_sum_full_biot$ssid != 308)

cor(tmp.df4_sum_full_biot1$arousal, tmp.df4_sum_full_biot1$Global.Mean.y, use = 'complete.obs')
```

>>>>

tmp.df4$trigger2 <- tmp.df4$trigger

@@

unique(tmp.df4$trigger2)
unique(tmp.df4$trigger)
unique(tmp.df4$tNo)

@@

db_beh2$triggeracq <- db_beh2$trigger
unique(db_beh2$ssid)

@@

Ledalab('/Users/heliocuve/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2])

@@

346, 351 - GP gsr data is messed up
- Note triggers need to be recreated here, never figured out why the digital events don't translate to ledalab

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021/Processed")

read_leda <- function(flnm) {
  data.table::fread(flnm) %>% 
    mutate(filename = flnm)
}

@@

db_leda$trigger<- as.numeric(db_leda$Event.NID)
unique(db_leda$trigger)

db_leda$ssid<- as.numeric(substr(db_leda$filename, 13,15))

colnames(tmp.df4_sum)
colnames(db_leda)

nrow(tmp.df4_sum)
nrow(db_leda)

colnames(tmp.df4_sum)

tmp.df4_sum2<- subset(tmp.df4_sum,tmp.df4_sum$tNo != -7)

tmp.df4_sum2<- tmp.df4_sum2%>%
  arrange(ssid, time, tNo)%>%
  group_by(ssid)%>%
  mutate(order = 1:n())

db_leda2<- subset(db_leda, db_leda$trigger != -7)

db_leda2<- db_leda2%>%
  arrange(ssid, Event.Nr)%>%
  group_by(ssid)%>%
  mutate(order = 1:n())

unique(db_leda2$order)

range(db_leda2$order, na.rm = TRUE)

# tmp.df4_sum_fullt<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
# tmp.df4_sum_full_backup<- tmp.df4_sum_full

@@

trigger<- db_leda2 %>%
  subset(ssid == 348)%>%
  select(order, Event.NID, trigger,Event.Nr)
```

@@

# check stiom screen
tmp.df4_sum_full_stim<- subset(tmp.df4_sum_full,  tmp.df4_sum_full$screencontent == 'stim')

# levels(as.factor(tmp.df4_sum_full_stim$Event.Name))

# exclude trials with very low gaze validity
tmp.df4_sum_full_stim<- subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$gaze_valid_prop> .85)
colnames(tmp.df4_sum_full_stim)

colnames(tmp.df4_sum_full)

```{r eval=FALSE, include=FALSE}

@@

ggplot(tmp.df4_sum_full_stim, aes(arousal_c, log1p(mean_fix_dur)))+
  geom_point()+
  geom_smooth(method = 'lm')
```

@@

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/IAPS/processed/345_456/CDA")

colnames(tmp.df4_sum_full)

@@

write_csv(db_leda_bio, 'db_leda_bio.csv')
write_csv(db_leda_bio, 'db_leda_bio_345_355_CDA.csv')

# db_leda_bio <- read_csv("db_leda_bio.csv")

colnames(db_leda_bio)

db_leda_bio$BIO_Event.NID<- db_leda_bio$Event.NID
db_leda_bio$BIO_filename <- db_leda_bio$filename

db_leda_bio$ssid<- as.numeric(substr(db_leda_bio$BIO_filename, 3,5))

unique(db_leda_bio$ssid)

unique(db_leda_bio$trigger)

# subset out rest period
db_leda_bio<- subset(db_leda_bio, Event.Nr>1)

db_leda_bio<- subset(db_leda_bio, CDA.nSCR!= "NaN")
range(db_leda_bio$Event.Nr)

# transform NaNs into proper NA
db_leda_bio[db_leda_bio == "NaN"] <- NA

# move counter to 1
range(db_leda_bio$Event.Nr-1)
range(db_leda_bio$Event.Nr)
trigger$Event.Nr<- NULL

db_leda_bio$order <- db_leda_bio$Event.Nr-1
db_leda_bio$trigger<- NULL

# merge trigger
trigger$Event.NID<- NULL
trigger$ssid<- NULL
View(db_leda_bio)

db_leda_bio$order
db_leda_bio<- left_join(db_leda_bio, trigger)

tmp.df4_sum_full

leda_bioames <- colnames(db_leda_bio)

newnames<- c("Event.Nr", paste0("BIO_", paste0(leda_bioames[2:21])))

newnames
db_leda_bio_backup<- db_leda_bio
names(db_leda_bio) <- newnames

db_leda_bio

db_leda_bio$ssid <- db_leda_bio$BIO_ssid

db_leda_bio$BIO_ssid<-NULL

db_leda_bio

tmp.df4_sum_full_bio<- left_join(tmp.df4_sum_full,  db_leda_bio)

@@

```{r eval=FALSE, include=FALSE}
# stim
db_leda_bio_stim<-subset(db_leda_bio, db_leda_bio$trigger< 100)
unique(db_leda_bio_stim$trigger)

colnames(tmp.df4_sum_full_stim_gp_leda_beh_self)
(unique(tmp.df4_sum_full_stim_gp_leda_beh_self$trigger))

db_leda_bio_stim$ssid<- as.character(db_leda_bio_stim$ssid)

# db_leda_bio_stim$trigger<- as.character(db_leda_bio_stim$trigger)

db_leda_bio$order<- db_leda_bio$Event.Nr

tmp.df4_sum_full_stim_gp_leda_beh_self$ssid<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$ssid)

tmp.df4_sum_full_stim_gp_leda_beh_self$trigger<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$trigger)

colnames(tmp.df4_sum_full_stim_gp_leda_beh_self)

@@

tmp.df4_sum_full_stim_gp_leda_beh_self<- tmp.df4_sum_full_stim_gp_leda_beh_self%>%
  arrange(ssid, tNo, Event.Nr)

db_leda_bio_stim<- db_leda_bio_stim%>%
  arrange(ssid, Event.Nr)

#tmp.df4_sum_full_bio$trigger<- tmp.df4_sum_full_bio$tNo
#tmp.df4_sum_full_bio$trigger<- if_else(tmp.df4_sum_full_bio$screencontent == 'fixation', 100,
 #                                      if_else(tmp.df4_sum_full_bio$screencontent == 'ValenceResp', 101,
                                               #if_else(tmp.df4_sum_full_bio$screencontent == #'IntResp', 102, #tmp.df4_sum_full_bio$tNo)))

unique(tmp.df4_sum_full_bio$trigger)
tmp.df4_sum_full_stim_gp_leda_beh_self$Event.Nr<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$Event.Nr)

db_leda_bio_stim$Event.Nr<- as.character(db_leda_bio_stim$Event.Nr)
View(tmp.df4_sum_full_stim_gp_leda_beh_self_biopac)

tmp.df4_sum_full_stim_gp_leda_beh_self_biopac<-left_join(tmp.df4_sum_full_stim_gp_leda_beh_self, db_leda_bio_stim, by = c("Event.Nr", "ssid"))

write_csv(tmp.df4_sum_full_stim_gp_leda_beh_self_biopac, 'tmp.df4_sum_full_stim_gp_leda_beh_self_biopac2.csv')

(db_leda_bio$trigger)

@@

ggplot(subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308), aes(TTP.AmpSum.y, arousal))+
  geom_point()+
  geom_smooth(method = 'lm', se = T)
ggplot(subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308 & tmp.df4_sum_full_biot$TTP.AmpSum.y> 0), aes( TTP.AmpSum.y, arousal))+
  geom_point()+
  geom_smooth(method = 'lm', se = T)

tmp.df4_sum_full_biot1 <-subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308)

cor(tmp.df4_sum_full_biot1$arousal, tmp.df4_sum_full_biot1$Global.Mean.y, use = 'complete.obs')

# now read them

# old
db_biohr <-
  list.files(pattern = "*.csv", 
             full.names = T) %>% 
  map_df(~read_biohr(.))

db_biohr$Order<- NULL
db_biohr$filename<- NULL
db_biohr$trigger<- as.factor(as.character(db_biohr$trigger))

unique(db_biohr$ssid)

db_biohr$ssid<- as.factor(as.character(db_biohr$ssid))

#HR BIOPAC

```{r}
library(readxl)
library(dplyr)
db_HR_bio <- read_excel("310_IAPS_Physio_HR.xls")

View(db_HR_bio)

nrow(db_HR_bio)

db_HR_bio<- db_HR_bio[6:nrow(db_HR_bio),]

library(data.table)
library(purrr)
# import
read_biohr <- function(flnm) {
  read_excel(flnm) %>% 
    mutate(filename = flnm)
}

# now read them
db_HR_bionew <-
  list.files(pattern = "*.xls", 
             full.names = T) %>% 
  map_df(~read_biohr(.))

db_HR_bio<- db_HR_bionew

unique(db_HR_bionew$filename)

test<- subset(db_HR_bio, db_HR_bio$filename == "./607_IAPS_Physio_HR.xls")

levels(as.factor(db_HR_bio$filename))
db_HR_bio$ssid<- substr(db_HR_bio $filename, 3,5)

db_HR_bio$filename<- NULL

db_HR_bio$`Stim-Response Analysis`

db_HR_bio$stim<- if_else(grepl('Stimulus', (db_HR_bio$`Stim-Response Analysis`)) == TRUE, db_HR_bio$`Stim-Response Analysis`, NULL)

library(tidyr)

db_HR_bio<- db_HR_bio%>%
  group_by(ssid)%>%
  fill(stim)

levels(as.factor(db_HR_bio$ssid))

#  remove na in the mean heart rate

db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$...2))

db_HR_bio$mhrtext<- is.character(db_HR_bio$...2)

db_HR_bio<- subset(db_HR_bio, !grepl('interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)

levels(as.factor(db_HR_bio$ssid))

# loosing participants here
View(db_HR_bio)

db_HR_bio<- subset(db_HR_bio, !grepl('Interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)

test<- subset(db_HR_bio, grepl('Interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
levels(as.factor(db_HR_biotest$ssid))

db_HR_bio<- subset(db_HR_bio, !grepl('Time', db_HR_bio$`Stim-Response Analysis`) == TRUE)

#db_HR_biotest1<- subset(db_HR_biotest, !is.na(db_HR_biotest$stim))

#test<- subset(db_HR_bio, db_HR_bio$ssid == 607)

levels(as.factor(db_HR_bio$ssid))

db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$`Stim-Response Analysis`))

db_HR_bio$...3<- NULL
db_HR_bio$...4<- NULL

db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$...2))

db_HR_bio<- subset(db_HR_bio, db_HR_bio$...2 != 'Mean(CH 40)')
db_HR_bio$timestart<- db_HR_bio$`Stim-Response Analysis`

db_HR_bio$Mean_HR<- db_HR_bio$...2

db_HR_bio<- db_HR_bio%>%
  arrange((as.numeric(timestart)), ssid)

db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$stim))

db_HR_bio$trigger<- substr(db_HR_bio$stim, 10,13)

unique((as.numeric(db_HR_bio$trigger)-128))

db_HR_bio$trigger_200<- if_else(db_HR_bio$trigger> 103, TRUE, FALSE)

db_HR_bio$trigger<- if_else(db_HR_bio$trigger_200 == TRUE, as.numeric(db_HR_bio$trigger)-128, as.numeric(db_HR_bio$trigger))

unique((as.numeric(db_HR_bio$trigger)))

#subset(db_HR_bio, db_HR_bio$ssid!= 328)%>%
#  group_by(timestart, ssid)%>%
 # mutate(EventNR= 1:225)

db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger< 100)

db_HR_bio1<- db_HR_bio1%>%
  arrange(as.numeric(timestart), ssid)

db_HR_bio1<- subset(db_HR_bio1,!is.na(db_HR_bio1$stim))

#tno
#subset(db_HR_bio1, db_HR_bio1$ssid != 328)%>%
table(is.na(db_HR_bio1$ssid))
db_HR_bio1<- db_HR_bio1%>%
  arrange(as.numeric(timestart), ssid)

db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)

db_HR_bio1no328<- db_HR_bio1no328 %>%
  group_by(as.numeric(ssid))%>%
  mutate(tNo = -6:49)

db_HR_bio328<-subset(db_HR_bio1, db_HR_bio1$ssid== 328)

db_HR_bio328<- db_HR_bio328 %>%
  group_by(as.numeric(ssid))%>%
  mutate(tNo = -6:24)

db_HR_bio2<- bind_rows(db_HR_bio1no328,db_HR_bio328)

colnames(db_HR_bio2)

levels(as.factor(db_HR_bio1no328$ssid))
db_HR_bio2$ssid<-db_HR_bio2$`as.numeric(ssid)`

#mereg old and new heart rate
# now read them
db_biohr$trigger

db_biohr$tno<-db_biohr$trigger
db_HR_bio2$trigger
colnames(db_biohr)

colnames(db_HR_bio2)

db_biohr$Mean_HR<- db_biohr$HR_BIO

db_biohr$timestart<- db_biohr$Time

left_join(db_HR_bio2, db_biohr)

db_HR_bio2<- select(db_HR_bio2, c(timestart,Mean_HR, tNo, ssid))

db_HR_bio2$`as.numeric(ssid)`<- NULL

str((db_HR_bio2))
str(db_biohrold2)
db_biohr$tNo<- db_biohr$tno
db_biohrold2<- db_biohr

db_biohrold2<- select(db_biohr, c(timestart,Mean_HR, tNo, ssid))
unique(db_biohrold2$tNo)

db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)
db_biohrold2$timestart<- as.numeric(db_biohrold2$timestart)

db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)
db_biohrold2$Mean_HR<- as.numeric(db_biohrold2$Mean_HR)

db_HR_bio2$tNo<- as.character(db_HR_bio2$tNo)
db_biohrold2$tNo<- as.character(db_biohrold2$tNo)
db_HR_bio2$ssid<- as.character(db_HR_bio2$ssid)

db_biohrold2$ssid<- as.character(db_biohrold2$ssid)

str(db_HR_bio2)

db_biohrold2test<- subset(db_biohrold2, db_biohrold2$tNo != 100)
db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 101)
db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 102)
db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 103)
db_HR_bio2$subj<- as.factor(db_HR_bio2$ssid)
db_biohrold2test$subj<- as.factor(db_biohrold2test$ssid)
db_biohrold2test$ssid<- NULL
db_HR_bio2$ssid<- NULL

str(db_HR_bio2)

db_HR_bio2<- db_HR_bio2[,1:4]

db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)

db_biohrold2test$Mean_HR<- as.numeric(db_biohrold2test$Mean_HR)

db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)

db_biohrold2test$timestart<- as.numeric(db_biohrold2test$timestart)

db_HR_bio_final<- bind_rows(db_HR_bio2, db_biohrold2test)

db_HR_bio_final$ssid<- db_HR_bio_final$subj
levels(as.factor(db_HR_bio_final$ssid))

db_HR_bio_final$subj<- NULL

write_csv(db_HR_bio_final, 'db_HR_bio_final_mar5.csv')

db_HR_bio1$tNo<- -6:49

db_HR_bio1$tNo<- if_else(db_HR_bio1$tNo< 0, as.numeric(db_HR_bio1$tNo), as.numeric(db_HR_bio1$tNo+1))

db_HR_bio1$
